### 2018-04-29 paper/related.tex
security discussion section

P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster), availability and replication (Gnutella), scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}, and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview). In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person. Here, we focus on sharing files in a more deliberate yet ad-hoc manner, i.e., between users that out-of-band agree to share a file but do not keep it available for anyone else in the future. TOR~\cite{Tor}, although not designed for file sharing specifically, comes closest in that respect, but does not address the following aspect.

>>>>

P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster), availability and replication (Gnutella), scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview). In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person. Here, we focus on sharing files in a more deliberate yet ad-hoc manner, i.e., between users that out-of-band agree to share a file but do not keep it available for anyone else in the future. TOR~\cite{Tor}, although not designed for file sharing specifically, comes closest in that respect, but does not address the following aspect.

### 2018-04-29 paper/security-analysis.tex
security discussion section

\section{Security analysis}%
\label{SecurityAnalysis}

\commentDaniel{Under editing.
  Must move suggestions for fixes to future work.}

@@

>>>>

\section{Security Discussion}%
\label{SecurityDiscussion}

@@

% \commentAL{To rewrite as real paragraphs} Future work and prospects:
% \begin{itemize}
% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
% 	\item Changing devices' asymmetric keys regularly would increase security.
% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver. To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.

% \end{itemize}

We see two alternative paths for improving the header.
First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
format to the routing of \(\SPOR\).
Then we could achieve the properties of Sphinx and enjoy provable security.

The second approach would be to use the technique by \textcite{PPACinPubFS}.
They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
things for different recipients.
This way we could have one ciphertext encrypted for all the alternative nodes 
--- across layers.
Then the ciphertext would decrypt to different plaintexts for nodes on different 
layers in the route.
This would hide the path length (constant-size ciphertexts by padding) and the 
position of individual nodes.
This approach would probably be the easiest, but would probably not provide all 
the properties from Sphinx (\eg resistance to active tagging attacks and bitwise 
unlinkability).
